`r glue::glue('inferCNV results for {params$library_id} with {params$reference_name} reference')`

### 2025-07-31 analyses/cell-type-consensus/exploratory-notebooks/02-explore-consensus-results.Rmd

```{r}
# list all results files 
results_files <- list.files(results_dir, pattern = "_consensus-cell-types\\.tsv.\\gz$", full.names = TRUE)

# get project ids from file list  
project_ids <- stringr::str_remove(basename(results_files), "_consensus-cell-types.tsv.gz")
names(results_files) <- project_ids

# remove cell line projects from file list
cell_line_projects <- c("SCPCP000020", "SCPCP000024")
project_ids <- setdiff(project_ids, cell_line_projects) # remove cell line projects
results_files <- results_files[project_ids]
```

@@

```{r, message=FALSE}
# read in diagnoses
diagnoses_df <- readr::read_tsv(diagnoses_file)

# read in results and prep data frame for plotting 
all_results_df <- results_files |> 
  purrr::imap(summarize_celltypes) |> 
  dplyr::bind_rows(.id = "project_id") |> 
  # add in diagnoses 
  dplyr::left_join(diagnoses_df, by = "project_id") |> 
  dplyr::mutate(
    # create a label for plotting
    project_label = glue::glue("{project_id}:{diagnosis}")
  )

@@

# get color palette
colors <- c(
  palette.colors(palette = "alphabet"),
  "black", # 1 extra since alphabet is 26 and we have 27, this will be plasma cell which shows up once 
  "grey60", 
  "grey95"
)
names(colors) <- c(unique_celltypes, "All remaining cell types", "Unknown")
```

>>>>

```{r}
# list all results files 
results_files <- list.files(results_dir, pattern = "_processed_consensus-cell-types\\.tsv.\\gz$", recursive = TRUE, full.names = TRUE)

# define cell line projects to remove
cell_line_projects <- c("SCPCP000020", "SCPCP000024")
```

@@

```{r, message=FALSE, warning=FALSE}
# read in diagnoses
diagnoses_df <- readr::read_tsv(diagnoses_file)

# read in results and prep data frame for plotting 
all_results_df <- results_files |> 
  purrr::imap(summarize_celltypes) |> 
  dplyr::bind_rows() |> 
  # remove cell line projects
  dplyr::filter(!project_id %in% cell_line_projects) |> 
  # add in diagnoses 
  dplyr::left_join(diagnoses_df, by = "project_id") |> 
  dplyr::mutate(
    # create a label for plotting
    project_label = glue::glue("{project_id}:{diagnosis}")
  )

@@

# get color palette
colors <- c(
  palette.colors(palette = "alphabet"),
  "lightyellow", # plasma cell 
  "black", # glial cell
  "grey60", 
  "grey95"
)
names(colors) <- c(unique_celltypes, "All remaining cell types", "Unknown")
```

### 2025-07-31 analyses/cell-type-consensus/exploratory-notebooks/03-osteosarcoma-consensus-celltypes.Rmd

```{r}
# list all results files 
results_files <- list.files(results_dir, pattern = "_consensus-cell-types\\.tsv.\\gz$", full.names = TRUE)

# get project ids from file list and assign as names
project_ids <- stringr::str_remove(basename(results_files), "_consensus-cell-types.tsv.gz")
names(results_files) <- project_ids

# grab only osteo projects
osteo_project_ids <- c("SCPCP000017", "SCPCP000018", "SCPCP000023")
results_files <- results_files[osteo_project_ids]

@@

```{r, message=FALSE}
# get immune cell types 
immune_df <- readr::read_tsv(consensus_immune_file)
immune_types <- immune_df$consensus_annotation

@@

# read in results and prep data frame for plotting 
all_results_df <- results_files |> 
  purrr::imap(summarize_celltypes) |> 
  dplyr::bind_rows(.id = "project_id") |> 
  # join with sample metadata
  dplyr::left_join(all_metadata_df, by = c("project_id", "library_id")) |>
  # remove pdx samples 
  dplyr::filter(sample_type != "patient-derived xenograft")
```

>>>>

```{r}
# grab only osteo projects
osteo_project_ids <- c("SCPCP000017", "SCPCP000018", "SCPCP000023")
osteo_results_dirs <- file.path(results_dir, osteo_project_ids)
# list all results files 
results_files <- osteo_results_dirs |> 
  list.files(pattern = "_processed_consensus-cell-types\\.tsv.\\gz$", recursive = TRUE, full.names = TRUE)

@@

```{r, message=FALSE, warning=FALSE}
# get immune cell types 
immune_df <- readr::read_tsv(consensus_immune_file)
immune_types <- immune_df$consensus_annotation

@@

# read in results and prep data frame for plotting 
all_results_df <- results_files |> 
  purrr::imap(summarize_celltypes) |> 
  dplyr::bind_rows() |> 
  # join with sample metadata
  dplyr::left_join(all_metadata_df, by = c("project_id", "library_id")) |>
  # remove pdx samples 
  dplyr::filter(sample_type != "patient-derived xenograft")
```

### 2025-07-31 analyses/infercnv-consensus-cell-type/exploratory-notebooks/SCPCP000004/01_nb-consensus-cell-types.Rmd

```{r}
options(readr.show_col_types = FALSE)
library(ggplot2)
theme_set(theme_bw())
```

@@

# The current results directory, found within the repository base directory
result_dir <- file.path(repository_base, "data", "current", "results")

# Path to cell-type-consensus results
consensus_dir <- file.path(result_dir, "cell-type-consensus", "SCPCP000004")

@@

```{r paths}
# Input consensus cell type files
celltype_files <- list.files(
  path = consensus_dir,
  pattern = "_processed_consensus-cell-types\\.tsv\\.gz$",
  recursive = TRUE,
  full.names = TRUE
) |>
  # set names as library id
  purrr::set_names(
    \(x) {
      stringr::str_split_i(basename(x), "_", 1)
    }
  )

@@

# Prepare data frame of all cell types
celltype_df <- celltype_files |>
  # consider only non-PDX
  purrr::keep_at(tumor_library_ids) |>
  purrr::map(readr::read_tsv) |>
  purrr::list_rbind() |>
  dplyr::select(library_id, barcodes, consensus_annotation) |>
  dplyr::left_join(cell_group_df, by = "consensus_annotation")
```

>>>>

```{r}
options(readr.show_col_types = FALSE)
suppressPackageStartupMessages({
  library(ggplot2)
  library(SingleCellExperiment)
})
theme_set(theme_bw())
```

@@

@@

```{r paths}
# Input sce files to get consensus cell types
sce_files <- list.files(
  path = data_dir,
  pattern = "_processed\\.rds$",
  recursive = TRUE,
  full.names = TRUE
) |>
  # set names as library id
  purrr::set_names(
    \(x) {
      stringr::str_split_i(basename(x), "_", 1)
    }
  )

@@

# Prepare data frame of all cell types
celltype_df <- sce_files |>
  # consider only non-PDX
  purrr::keep_at(tumor_library_ids) |>
  purrr::map(
    \(sce_file) {
      readRDS(sce_file) |>
        colData() |>
        as.data.frame() |>
        dplyr::select(
          barcodes, 
          consensus_annotation = consensus_celltype_annotation
        )
  }) |>
  purrr::list_rbind(names_to = "library_id") |>
  dplyr::left_join(cell_group_df, by = "consensus_annotation")
```

### 2025-07-31 analyses/infercnv-consensus-cell-type/template-notebooks/SCPCP000015_explore-infercnv-results.Rmd

```{r base paths}
# repo and analysis base dirs
repository_base <- rprojroot::find_root(rprojroot::is_git_root)
analysis_dir <- file.path(repository_base, "analyses", "infercnv-consensus-cell-type")

>>>>

```{r base paths}
# repo and analysis base dirs
module_base <- rprojroot::find_root(rprojroot::is_renv_project)
repository_base <- file.path(module_base, "..", "..") # we can't use `rprojroot::is_git_root` in Docker, so back up to OpenScPCA base
analysis_dir <- file.path(repository_base, "analyses", "infercnv-consensus-cell-type")
